APIs for hyperparameter optimization in scikit-learn

### 2013-05-12 paper.tex
start section about nested pipelines

>>>>

\subsection{Recursive pipelines}

In some cases, it is useful to build recursive pipelines,
and scikit-learn has support for these:
pipelines are themselves estimators,
and can thus be nested inside larger pipelines.

While direct use of this idiom would not have any benefit
over using the individual stages of the sub-pipeline directly,
the recursion support shines when in more complex situations
that involve the construction of estimators using \textit{meta-estimators}.
These are objects in the scikit-learn API
that wrap an estimator to give it additional functionality.
An example of meta-estimators are object of the class
\texttt{OneVsRestClassifier},
which can be used to construct a multi-label classifier
\citep{tsoumakas2007multi}
from an ordinary binary classifier object
by constructing one binary classifier per class
(a strategy variously called one-vs.-the-rest,
one-vs.-all or binary relevance).

% TODO insert example from http://stackoverflow.com/q/16437022/166749 here
